Corotating Dust Clumps Around Adolescent M-Dwarfs: Four Years of TESS

### 2023-06-27 paper/ms.tex
update ms

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f2.pdf}
    \vspace{-0.7cm}
		\caption{
      {\bf CQVs found in the TESS 2-minute data at
      $d$$<$150\,pc, acquired between July~2018 and Sep~2022.}
      Phased TESS light curves over one month are shown for \ngoods\
      CQVs.
      Gray are raw 2-minute data;
			black bins to 300 points per cycle.  Each panel is labelled by
      the TIC identifier, the TESS sector number, and the period in hours.
      The ordering is discussed in Section~\ref{sec:catalog}
		}
		\label{fig:singlemosaic}
	\end{center}
\end{figure*}

@@

The prominence scenario, in a broad sense, argues that some intrinsic
stellar process is key for generating the CQV phenomenon.
If this were true, then stars of identical mass, size, and rotation
periods might be expected to show the phenomenon in equal number --
independent of age.
This is because the stellar dynamo for M-dwarfs is generated by fluid
motions inside the star, which should be identical for stars of the
same mass, size, and rotation period.

@@

However there are two glaring issues with the disintegrating planetesimal swarm idea.
First, a large number of the dips show asymmetries in the {\it wrong
	direction} relative to the naive expectation of a trailing comet tail.
Dust forward scattering might be one possible way out; so too might
invoking non-exponentially decaying dust
distributions as a function of azimuth.
Second, and perhaps more serious, a planetesimal swarm should be expected
to be {\it exactly periodic} over observable timescales, on the presumption that the planetesimals
would be massive enough to not feel any headwind or magnetic field.
This is not what is observed; instead, every dip period
that is observed to be distinct from the fundamental 18.5611\,hr period
is both short-lived, and unique.
This suggests structures much less massive than a 1--100\,km sized
planetesimal,
 more strongly
which could be more strongly influenced by the stellar magnetic field.

@@

Many questions remain.
After correcting for line-of-sight inclination, are
most young M-dwarfs CQVs?  What observational signatures distinguish
the proposed models (Figure~\ref{fig:f1}, bottom row)?  What
organizational regularities characterize the CQV as a class of
variable star?  What physically sets the extremes of the CQV population, such as
the longest rotation periods, hottest stellar temperatures, and oldest
stellar ages?  And finally, what connections, if any, do CQVs have to
topics such as stellar evolution, M-dwarf magnetic fields, debris
disks, and close-in exoplanets?
While we have tried to point out possible connections, the most
likely path toward definitive resolutions would be to observe a full
phase curve of LP 12-502 using JWST/MIRI.

>>>>

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f2.pdf}
    \vspace{-0.7cm}
		\caption{
      {\bf CQVs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CQVs.
      Gray are raw 2-minute data;
			black bins to 300 points per cycle.  Each panel is labelled by
      the TIC identifier, the TESS sector number, and the period in hours.
      The ordering is discussed in Section~\ref{sec:catalog}
		}
		\label{fig:singlemosaic}
	\end{center}
\end{figure*}

@@

The prominence scenario, in a broad sense, argues that some intrinsic
stellar process is key for generating the CQV phenomenon.
If this were true, then stars of identical mass, size, and rotation
periods might be expected to show the phenomenon in equal number --
irrespective of age.
This is because the stellar dynamo is generated by fluid
motions inside the star, which should be identical for stars of the
same mass, size, and rotation period.

@@

However there are two glaring issues with the disintegrating planetesimal swarm idea.
First, a large number of the dips show asymmetries in the {\it wrong
	direction} relative to the naive expectation of a trailing comet tail.
Dust forward scattering might be one possible way out; so too might
invoking non-exponentially decaying dust
distributions as a function of azimuth.
Second, and perhaps more serious, the (unseen) planetesimals 
should
be on {\it exactly periodic} orbits over observable timescales, on the presumption that the planetesimals
would be massive enough to not feel any headwind or magnetic field.
This is not what is observed; instead, every dip period
that is observed to be distinct from the fundamental 18.5611\,hr period
is both short-lived, and unique.
The fundamental 18.5611\,hr period itself is itself associated with
material at too many phases to arguably be tied to a single launching body.
This suggests that the dust clumps must be much less massive than a 1--100\,km sized
planetesimal,
and therefore more easily influenced by the stellar magnetic field, and events
like flares.

@@

Many questions remain.
After correcting for line-of-sight inclination, are
most young M-dwarfs CQVs?  What observational signatures distinguish
the proposed models (Figure~\ref{fig:f1}, bottom row)?  What
organizational regularities characterize the CQV as a class of
variable star?  What physically sets the extremes of the CQV population, such as
the longest rotation periods, hottest stellar temperatures, and oldest
stellar ages?  And finally, what connections, if any, do CQVs have to
topics such as stellar evolution, M-dwarf magnetic fields, debris
disks, and close-in exoplanets?
While we have tried to point out possible connections, the most
likely path toward definitive resolutions would be to observe a full
phase curve of LP 12-502, or perhaps some other suitable object, using JWST/MIRI.
